### 2014-02-27 paper/retrofit.tex
english

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
Using this definition, we can no expand the definition for the
specification family of languages.
%
Specifically, |specLang alpha (targetLang nop) = (ifc C, ifc V, .->,
erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and $|ifc V|
= |iS| \times |it|^*$, where $|it|^* \subset |it|$ it the type for
tasks whose expressions have been reduced to values.\footnote{
Here we abuse notation by using metavariables to describe types that
we previously, e.g., |it| for the type of task.
}
%}

>>>>

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
Using this definition, we can now expand the definition for the
specification family of languages.
%
Specifically, |specLang alpha (targetLang nop) = (ifc C, ifc V, .->,
erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and $|ifc V|
= |iS| \times |it|^*$, where $|it|^* \subset |it|$ it the type for
tasks whose expressions have been reduced to values.\footnote{
Here, we abuse notation by using metavariables to describe types of
the corresponding non-terminals, e.g., |it| for the type of task.
}
%}
